The development of infants' responses to mispronunciations: A Meta-Analysis

### 2019-05-24 VonHolzenBergmann_MPMetaAnalysis.tex
moderator analysis results completed

Although all mispronunciation sensitivity studies are generally
interested in the the phonological detail with which infants represent
familiar words, many studies pose more nuanced questions. These
questions concern issues at the intersection of phonological development
and lexical processing and often result in manipulations of the stimuli
and experimental procedure. Next to the core investigation of the shape
of development of infants' mispronunciation sensitivity, we take the
opportunity of a systematic aggregation of data to address these
questions and the influence of these manipulations on infants' ability
to detect mispronunciations and how this may change with development.

@@

 &  &  &  & \multicolumn{1}{c}{Distractor} & & \multicolumn{3}{c}{Mispronunciation}  &\\
\cmidrule(r){5-5} \cmidrule(r){7-9}

@@

We separated conditions according to whether or not the target word was
mispronounced to be able to investigate infants' looking to the target
picture as well as their mispronunciation sensitivity, which is the
difference between looks to the target in correct and mispronounced
trials. When the same infants were further exposed to multiple
mispronunciation conditions and the results were reported separately in
the paper, we also entered each condition as a separate row (e.g.,
consonant versus vowel mispronunciations; Mani \& Plunkett, 2007). The
fact that the same infants contributed data to multiple rows (minimally
those containing information on correct and mispronounced trials) leads
to shared variance across effect sizes, which we account for in our
analyses (see next section). We will call each row a record; in total
there were 251 records in our data.

@@

\subsubsection{Interim Discussion}\label{interim-discussion}

The main goal of this paper was to assess mispronunciation sensitivity
and its maturation with age and increased vocabulary size. The results
seem clear: Although infants consider a mispronunciation to be a better
match to the target image than to a distractor image, there was a
constant and stable effect of mispronunciation sensitivity. This did not
change with development, and we might consider age a proxy for
vocabulary size. We observe that the data for directly reported
vocabulary size were too sparse to draw strong conclusions. Of the three
predictions about the development of infants' sensitivity to
mispronunciations discussed in the Introduction, the present results
lend some support for the proposal that mispronunciation sensitivity
stays consistent as infants develop. This runs counter to existing
theories of phono-lexical development, which predict either an increase
(Curtin \& Werker, 2007; Curtin, Byers-Heinlein, \& Werker, 2011; Werker
\& Curtin, 2005) or decrease (Best, 1994, 1995) in mispronunciation
sensitivity. Furthermore, although we found a relationship between
vocabulary size (comprehension) and target looking for correct
pronunciations, we found no relationship between vocabulary and target
looking for mispronunciations. This also runs counter to the predictions
for the PRIMR (Curtin \& Werker, 2007; Curtin et al., 2011; Werker \&
Curtin, 2005) and Assimilation (Best, 1994, 1995) models, but may be due
to our analyses being underpowered. In sum, it seems that current
theories of infants' phono-lexical development cannot fully capture our
results, but that more investigation is needed to draw a firm
conclusion.

@@

We next evaluated the developmental trajectory of infants'
mispronunciation sensitivity. Based on previous theoretical accounts and
existing experimental evidence, we envisioned three possible
developmental patterns: increasing, decreasing, and unchanging
sensitivity. We observed no influence of age when it was considered as a
moderator of mispronunciation sensitivity. Of the two mainstream
theories identified in our literature review, neither the Perceptual
Attunement account (Best, 1994, 1995) nor PRIMIR (Curtin \& Werker,
2007; Curtin et al., 2011; Werker \& Curtin, 2005) account for a lack of
developmental change. The results of our meta-analysis are reflecting a
pattern previously reported by a handful of studies directly comparing
infants over a range of ages (Bailey \& Plunkett, 2002; Swingley \&
Aslin, 2000; Zesiger et al., 2012), which also found no developmental
change in mispronunciation sensitivity.

>>>>

Although all mispronunciation sensitivity studies are generally
interested in the the phonological detail with which infants represent
familiar words, many studies pose more nuanced questions. These
questions concern issues at the intersection of phonological development
and lexical processing and often result in manipulations of the stimuli
and experimental procedure. These manipulations may impact our overall
estimate of the effect size of mispronunciation sensitivity. Next to the
core investigation of the shape of development of infants'
mispronunciation sensitivity, we take the opportunity of a systematic
aggregation of data to address these questions and the influence of
these manipulations on infants' ability to detect mispronunciations and
how this may change with development.

@@

 &  &  &  & \multicolumn{2}{c}{Distractor} & \multicolumn{3}{c}{Mispronunciation}  &\\
\cmidrule(r){5-6} \cmidrule(r){7-9}

@@

A detailed explanation for moderating factors 3-8 can be found in their
respective sections in the Results. We separated conditions according to
whether or not the target word was mispronounced to be able to
investigate infants' looking to the target picture as well as their
mispronunciation sensitivity, which is the difference between looks to
the target in correct and mispronounced trials. When the same infants
were further exposed to multiple mispronunciation conditions and the
results were reported separately in the paper, we also entered each
condition as a separate row (e.g., consonant versus vowel
mispronunciations; Mani \& Plunkett, 2007). The fact that the same
infants contributed data to multiple rows (minimally those containing
information on correct and mispronounced trials) leads to shared
variance across effect sizes, which we account for in our analyses (see
next section). We will call each row a record; in total there were 251
records in our data.

@@

\subsubsection{Interim Discussion:
Meta-Analysis}\label{interim-discussion-meta-analysis}

The main goal of this paper was to assess mispronunciation sensitivity
and its maturation with age and increased vocabulary size. The results
seem clear: Although infants consider a mispronunciation to be a better
match to the target image than to a distractor image, there was a
constant and stable effect of mispronunciation sensitivity. This did not
change with development, and we might consider age a proxy for
vocabulary size. We observe that the data for directly reported
vocabulary size were too sparse to draw strong conclusions. In the
literature, evidence for all possible developmental trajectories has
been found, including mispronunciation sensitivity that increases,
decreases, or does not change with age or vocabulary size. The present
results do lend some support for the proposal that mispronunciation
sensitivity stays consistent as infants develop. Furthermore, although
we found a relationship between vocabulary size (comprehension) and
target looking for correct pronunciations, we found no relationship
between vocabulary and target looking for mispronunciations. This may be
due to too few studies including reports of vocabulary size and more
investigation is needed to draw a firm conclusion.

Alternatively, the lack of developmental change in mispronunciation
sensitivity could be due to differences in the types of tasks given to
infants of different ages. If infants' word recognition skills are
generally thought to improve with age and vocabulary size, research
questions that tap more complex processes may be more likely to be
investigated in older infants. In the following section, we investigate
the role that different moderators play in mispronunciation sensitivity.
To investigate the possibility of systematic differences in the tasks
across ages, we additionally include an exploratory analysis of whether
different moderators and experimental design features were included at
different ages.

\subsection{Moderator Analyses}\label{moderator-analyses}

In this section, we consider each moderator individually and investigate
its influence on mispronunciation sensitivity. For most moderators
(except Number of features changed), we combine the correct and
mispronounced datasets and include the moderator of condition, to study
mispronunciation sensitivity as opposed to object recognition. To better
understand the impact of these moderators on developmental change, we
include age as subsequent moderator as well as an exploratory analysis
of the age of infants tested with each type of moderator. The latter
analysis is included to explore whether the lack of developmental change
in mispronunciation sensitivity in the overall dataset is due to more
complex moderator tasks being given to older infants, which may lower
the overall effect size of mispronunciation sensitivity at older ages
and dampen any evidence of change.

\subsubsection{Number of features
changed}\label{number-of-features-changed}

To assess whether the number of features changed modulates
mispronunciation sensitivity, we calculated the meta-analytic effect for
object identification in response to words that were pronounced
correctly and mispronounced using 1-, 2-, and 3-feature changes. We did
not include data for which the number of features changed in a
mispronunciation was not specified or the number of features changed was
not consistent (e.g., one mispronunciation included a 2-feature change
whereas another only a 1-feature change). This analysis was therefore
based on a subset of the overall dataset, with 81 experimental
conditions for correct pronunciations, 108 for 1-feature
mispronunciations, 16 for 2-feature mispronunciations, and 6 for
3-feature mispronunciations. Each feature change (from 0 to 3; 0
representing correct pronunciations) was considered to have an equal
impact on mispronunciation sensitivity, following the argument of graded
sensitivity (White \& Aslin, 2008; Mani \& Plunkett 2011), and this
modertor was coded as a continuous variable.

To understand the relationship between number of features changed and
mispronunciation sensitivity, we evaluated the effect size Hedges'
\emph{g} with number of features changed as a moderator. The moderator
test was significant, QM(1) = 137.214, \emph{p} \textless{} .001.
Hedges' \emph{g} for number of features changed was -0.306 (SE = 0.026),
which indicated that as the number of features changed increased, the
effect size Hedges' \emph{g} significantly decreased (CI {[}-0.357,
-0.255{]}, \emph{p} \textless{} .001). We plot this relationship in
Figure \ref{fig:PlotFeatEffect}. This confirms previous findings of a
graded sensitivity to the number of features changed for both consonant
(White \& Morgan, 2008) and vowel (Mani \& Plunkett, 2011)
mispronunciations as well as the importance of controlling for the
degree of phonological mismatch in experimental design.

\subsection{(Insert Figure \ref{fig:PlotFeatEffect} about
here)}\label{insert-figure-reffigplotfeateffect-about-here}

\begin{figure}
\centering
\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotFeatEffect-1.pdf}
\caption{}
\end{figure}

\begin{verbatim}
## pdf 
##   2
\end{verbatim}

@@

We next evaluated the developmental trajectory of infants'
mispronunciation sensitivity. Based on previous theoretical accounts and
existing experimental evidence, we envisioned three possible
developmental patterns: increasing, decreasing, and unchanging
sensitivity. We observed no influence of age when it was considered as a
moderator of mispronunciation sensitivity. Of the two mainstream
theories identified in our literature review, neither the Perceptual
Attunement account (Best, 1994, 1995) nor PRIMIR (Curtin \& Werker,
2007; Curtin, Byers-Heinlein, \& Werker, 2011; Werker \& Curtin, 2005)
account for a lack of developmental change. The results of our
meta-analysis are reflecting a pattern previously reported by a handful
of studies directly comparing infants over a range of ages (Bailey \&
Plunkett, 2002; Swingley \& Aslin, 2000; Zesiger et al., 2012), which
also found no developmental change in mispronunciation sensitivity.
